# Code availability {#sec-code}

<!--
The following reproducibility statement template is courtesy of Rob J. Hyndman and his Monash thesis template at https://robjhyndman.com/hyndsight/quarto_templates.html.

Though it is recommended to include such a statement, the statement is optional and it should not be included if not true!

You can learn more about the **renv** package here:
https://rstudio.github.io/renv/articles/renv.html
-->

This thesis is written using Quarto with **renv** [@renv] to create a reproducible environment. All materials (including the data sets and source files) required to reproduce this document can be found at the Github repository [github.com/GITHUB-USERNAME/THESIS-REPO-NAME](https://github.com/github-username/thesis-repo-name). 

This work is licensed under a [Creative Commons  Attribution-NonCommercial-ShareAlike 4.0 International License](http://creativecommons.org/licenses/by-nc-sa/4.0/).


<!--
Include all source code below, preferably with a separate subsection per chapter. 

The `save-code-chunks-to-scripts` code chunk will generate R scripts from the code chunks in the specified qmd files. Those R scripts will then be sourced and printed (but not evaluated) in the corresponding subsections below. CAUTION: `knitr::purl()` will pull in ALL code chunks, even if they are not evaluated. Be sure to remove any unevaluated code chunks prior to your final thesis submission.
-->

```{r}
#| label: save-code-chunks-to-scripts
#| include: false

# ==============================================================================
# RUN THIS CHUNK PRIOR TO RENDERING BOOK TO CREATE FIRST VERSION OF R SCRIPT(S).
# ==============================================================================
# Oddly, this code seems to run *after* the rendering process, so you will need
# to run this chunk once to create an initial version of the R script(s). 
# After that, the R scripts will automatically update when you re-render the book.
# You may have to render twice for updated code to appear in the rendered PDF---
# Run 1 updates the script(s), Run 2 shows the updated script(s) in the book.
# Alternatively, you can run this code chunk to update any script(s) prior to
# rendering the PDF. 
# ==============================================================================

# Save Ch 2 qmd code chunks to R script
knitr::purl(input = "02-ch2-simple-example.qmd",
            output = "source/temp03-code-chunks-ch2.R", 
            # documentation values:
            # 1 = include chunk options when rendering (recommended default)
            #     (long dashed horizontal line will shorten after re-rendering)
            # 0 = include code only
            documentation = 1)

# Repeat for each chapter with code chunks, and then source the R scripts
# in the relevant subsections below.

```




## Code from @sec-simple

### Code required to clean WNBA data

```{r}
#| label: print-wrangling-code
#| echo: true
#| eval: false

{{< include source/temp01-clean-wnba.R >}}
```

### Code used to generate tables and figures

```{r}
#| label: print-ch2-code-chunks
#| echo: true
#| eval: false

{{< include source/temp03-code-chunks-ch2.R >}}
```



## Code for simulation study

```{r}
#| label: print-simulation-code
#| echo: true
#| eval: false

{{< include source/temp02-hello.R >}}
```



