# Code availability {#sec-code}

<!--
The following reproducibility statement template is courtesy of Rob J. Hyndman and his Monash thesis template at https://robjhyndman.com/hyndsight/quarto_templates.html.

Though it is recommended to include such a statement, the statement is optional and it should not be included if not true!

You can learn more about the **renv** package here:
https://rstudio.github.io/renv/articles/renv.html
-->

This thesis is written using Quarto with **renv** [@renv] to create a reproducible environment. All materials (including the data sets and source files) required to reproduce this document can be found at the Github repository [github.com/GITHUB-USERNAME/THESIS-REPO-NAME](https://github.com/github-username/thesis-repo-name). 

This work is licensed under a [Creative Commons  Attribution-NonCommercial-ShareAlike 4.0 International License](http://creativecommons.org/licenses/by-nc-sa/4.0/).


<!--
Include all source code below.

Unfortunately, the `ref-label: !expr knitr::all_labels()` code chunk option (see the end of `02-ch2-simple-example.qmd` for an example) can print all code within the same .qmd file but *cannot* pull code from other .qmd files within a project (see https://github.com/quarto-dev/quarto-cli/discussions/6650). 


If you don't want to use that approach to display the source code at the end of each individual chapter, then you can manually copy and paste code chunks here, preferably one subsection per chapter. For example:

## Source code for chapter 2:

### Code used to generate tables and figures 
```{r}
#| echo: true
#| eval: false

Paste your R code
```

### Code sourced from external scripts

```{r}
#| echo: true
#| eval: false

{{< include source/temp01-clean-wnba.R >}}
```

-->


## Code sourced from external scripts

```{r}
#| echo: true
#| eval: false

{{< include source/temp01-clean-wnba.R >}}
```

```{r}
#| echo: true
#| eval: false

{{< include source/temp02-hello.R >}}
```


